---
name: Thomas R. Vargas
www: thomasrvargas.com
email: "thomasvargasc@gmail.com"
github: thomasvargas
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
headcolor: 414141

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Academic Appointments

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Postdoctoral Fellow", "McMaster University", "Hamilton, ON", "June 2020 - Present", "A variety of consulting projects with substantial spatio-temporal modelling tasks.",
) %>% 
  detailed_entries(role, dates, company, loc)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD in Political Science", "2020", "University of Minnesota", "Minneapolis, MN",
  "Master of Public Policy", "2012", "The College of William & Mary", "Williamsburg, VA",
  "BS in Foreign Service", "2010", "Georgetown University", "Washington, DC"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Professional Experience

```{r work}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, 
  "Editorial Assistant", "American Political Science Review", "Hamilton, ON", "June 2020 - Present",
  "Visiting Scholar", "Sanford School of Public Policy, Duke University", "Durham, NC", "2019-2020",
  "Managing Editor", "Comparative Political Studies", "Minneapolis, MN", "2016-2018",
  "Policy and Training Analyst", "Abdul Latif Jameel Poverty Action Lab (J-PAL)", "Santiago, Chile", "2012-2014",
) %>% 
  detailed_entries(role, dates, company, loc)
```

# Publications

Vargas, Thomas R. 2020. ``Flying Blind: Education Reform in Latin America in the 1990s.'' \textit{International Journal of Education Reform}. Forthcoming. 

# Working Papers

Samuels, David and Thomas R. Vargas. ``Democracy, Land Inequality, and Human Capital Formation.”

Vargas, Thomas R. ``The Political Origins of Education Reform.”

Vargas, Thomas R. ``Slow Burn: The Incremental Effect of Unions on Social Spending in Latin America."

# Awards and Fellowships

```{r awards}
tribble(
  ~ company, ~ loc, 
  "Doctoral Dissertation Fellowship 2019-2020", "University of Minnesota",
  "Dissertation Research Fellowship 2018", "University of Minnesota",
  "David and Janis Larson Graduate Research Fellowship in Political Economy 2016-2017", "University of Minnesota",
  "Robert and Shirley Holt Discovery Fellowship 2014-2015", "University of Minnesota",
  "Outstanding Graduate Assistant Award 2011 & 2012", "The College of William & Mary"
) %>% 
  detailed_entries(company, loc)
```

# Skills and Languages

Spanish; R, Stata, Python, Git, LaTex

# Teaching Experience

## Primary Instructor

```{r}
tribble(
  ~Year, ~Name, ~Duty,
  '2018', "Political Economy of Development","s",
) %>% 
  detailed_entries(
    where = Year,
    with = Name
  )
```

## Teaching Assistant

```{r}
tribble(
  ~Year, ~Name,
  'University of Minnesota, 2015', "Puzzles in World Politics", 
  'University of Minnesota, 2016',"Struggles and Issues in the Middle East",
  'J-PAL, 2012-2014', "Evaluating Social Programs",
) %>% 
  detailed_entries(
    where = Year,
    with = Name
  )
```
# References

```{r}
tribble(
  ~Name, ~Title, ~Contact,
  'David Samuels',  "Distinguished McKnight University Professor, University of Minnesota", "dsamuels@umn.edu",
  'Teri Caraway',  "Professor of Political Science,  University of Minnesota", "caraway@umn.edu",
  'John Freeman',  "John Black Johnston Distinguished Professor, University of Minnesota", "freeman@umn.edu"
) %>% 
  detailed_entries(
    where = Contact,
    with = Name, 
    what = Title
  )

